Manuscript Figures for Genome Biology

### 2018-07-23 manuscript_figures/manuscript_figures.Rmd
Remove points from case study vs sim boxplot fig

ggplot(rank.tab , 
       aes(y = prop_casestudy, x = method, group = method, color = Method)) +
  geom_boxplot(aes(x = prop_yeastsim, group = as.factor(prop_yeastsim), y = prop_casestudy),
                   alpha = 0.3, width = 0.04, outlier.shape = NA) +
  geom_quasirandom(aes(x = prop_yeastsim, y = prop_casestudy, color = Method, shape = casestudy),
                   alpha = 0.6, cex=3, width = 0.002,  groupOnX = TRUE,
                   varwidth = TRUE) +
  scale_color_manual(values=col) +
  theme_bw() +
  xlab("Proportion of maximum rejections in yeast simulation (n=5)") +  
  ylab("Proportion of maximum rejections in casestudies") +
  labs(shape = "Case Study") 
ggsave(file.path(outdir, "Figure_simVcasestudyRanks_points.pdf"), width=6, height=4)

>>>>

ggplot(rank.tab , 
       aes(y = prop_casestudy, x = method, group = method, color = Method)) +
  geom_boxplot(aes(x = prop_yeastsim, group = as.factor(prop_yeastsim), y = prop_casestudy),
                   alpha = 0.3, width = 0.04, outlier.shape = NA) +
  scale_color_manual(values=col) +
  theme_bw() +
  xlab("Proportion of maximum rejections in yeast simulation (n=5)") +  
  ylab("Proportion of maximum rejections in casestudies") +
  labs(shape = "Case Study") 
ggsave(file.path(outdir, "Figure_simVcasestudyRanks_points.pdf"), width=6, height=4)
